---
title: "COMPSCIX 415.2 Homework 4"
author: "James Harrison"
date: "2/24/2018"
output: html_document
self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(nycflights13)
library(tidyverse)
```

<h1>Homework 4</h1>
<h3>Section 5.6.7: #2, #4, #5 and #6 only</h3>
2. We could write it using group by tailnum, then summarize and use the sum of the distance to equal n. 
```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>% count(tailnum, wt = distance)
```

```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))
  
not_cancelled %>%
  group_by(tailnum) %>%
  summarise( 
           n = sum(distance)
          )
```
<br><br>
4. Cancelled flights to average delay - yes there is a correlation between the longer delays and more cancelled flights.
```{r}
cancelled <- flights %>% 
  filter(is.na(dep_delay), is.na(arr_delay))

  #daily <- group_by(flights, year, month) #%>%
 # filter(is.na(dep_delay), is.na(arr_delay))
#(per_month   <- summarise(daily, flights = n(), delay = mean(arr_delay)))


#by_month <- group_by(flights, year, month)
#summarize(by_month,
                        # count = n(),
                        # arr_delay = mean(arr_delay, na.rm = TRUE),
                        # dep_delay = mean(dep_delay, na.rm = TRUE),
                        # )

james_flights <- flights %>% 
  mutate(cancel = (is.na(dep_delay) | is.na(arr_delay))) %>%
  group_by( year, month, day)%>%
  summarize(
      arr_delay = mean(arr_delay, na.rm = TRUE),
      cancelled = mean(cancel)
  ) 
  ggplot(james_flights, aes(x=arr_delay, y=cancelled))+
    geom_point()


```
<br><br>
5. F9 has the worst delays, but if we add in the destination as well United to STL is the worst route.
```{r}
new_flights <- flights %>% group_by(carrier, dest) %>% summarise(n(), arr_delay = mean(arr_delay, na.rm = TRUE))
arrange(new_flights, desc(arr_delay))

```
<br><br>
6. If sort is on it will sort in descending value of N - could be useful when trying to see the greatest number of delays by carrier for example.
<br><br>

<h3>Section 10.5: #1, #2, #3 and #6 only</h3>
1. When printing a tibble only prints the first ten rows and each column prints both name and type.
<br><br>
2. Tibbles let you quickly pull out data by name with tools like $ and [|]. In the example you can quickly see variable x in df using $. Tibbles are also more strict - they won't do partial matching and warn you if the column you're accessing doesn't exist.
<br><br>
3. Use the $ tool - can grab variables by name.
6. The tibble.max_extra_cols controls extra columns printed in a tibble.
<br><br>

<h3>Section 12.3.3: #2, #3 and #4 only</h3>
2. You need the numbers in quotations.
<br><br>
3. It fails because it has multiple values for one type - philip woods has two ages - if we add another column for age 1 and age 2 it could work.
<br><br>
4. We need to gather the tibble - the variables are the pregnant true false, a gender, and a count of how many are in each category.
```{r}
preg <- tribble(
  ~pregnant, ~male, ~female,
  "yes",     NA,    10,
  "no",      20,    12
)

gather(preg, gender, count, male, female)
```
<br><br>
<h3>Section 12.4.3: #1 and #2 only</h3>
1. In separate() - extra can be used to control what happens when separating a character vector with extra values- you can warn, drop, or merge the extra values. Fill can be used in the opposite case when there aren't enough values - you can warn, fill right with missing values or fill left with missing values.
<br><br>
2. Remove gets rid of the original input column you're working with - you'd keep it as false if you want to maintain that column as well. 

