---
title: "COMPSCIX 415.2 Homework 4"
author: "James Harrison"
date: "2/24/2018"
output: html_document
self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(nycflights13)
library(tidyverse)
```

<h1>Homework 4</h1>
<h3>Section 5.6.7: #2, #4, #5 and #6 only</h3>
2. We could write it using group by tailnum, then summarize and use the sum of the distance to equal n. 
```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))

not_cancelled %>% count(tailnum, wt = distance)
```

```{r}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))
  
not_cancelled %>%
  group_by(tailnum) %>%
  summarise( 
           n = sum(distance)
          )
```
<br><br>
4. Cancelled flights to average delay
```{r}
cancelled <- flights %>% 
  filter(is.na(dep_delay), is.na(arr_delay))

  #daily <- group_by(flights, year, month) #%>%
 # filter(is.na(dep_delay), is.na(arr_delay))
#(per_month   <- summarise(daily, flights = n(), delay = mean(arr_delay)))


by_month <- group_by(flights, year, month)
summarize(by_month,
                         count = n(),
                         arr_delay = mean(arr_delay, na.rm = TRUE),
                         dep_delay = mean(dep_delay, na.rm = TRUE),
                         )
```
<br><br>
5. F9 has the worst delays, but if we add in the destination as well United to STL is the worst route.
```{r}
new_flights <- flights %>% group_by(carrier, dest) %>% summarise(n(), arr_delay = mean(arr_delay, na.rm = TRUE))
arrange(new_flights, desc(arr_delay))

```
<br><br>
6. If sort is on it will sort in descending value of N - could be useful when trying to see the greatest number of delays by carrier for example.
<br><br>

<h3>Section 10.5: #1, #2, #3 and #6 only</h3>
1. 
