---
title: "COMPSCIX 415.2 Homework 8"
author: "James Harrison"
date: "3/25/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(broom)
library(rpart)
library(partykit)
library(ROCR)
```

#Homework 8 - the final HW!
###Excercise 1
There are 891 observations for 12 variables.
```{r}
train_t <- read.csv(file = "/Users/james.harrison/compscix-415-2-assignments/train_titanic.csv") %>% mutate(
  Survived = factor(Survived)
)
glimpse(train_t)

```

###Excercise 2
```{r}
# load packages
library(broom)
# When taking a random sample, it is often useful to set a seed so that
# your work is reproducible. Setting a seed will guarantee that the same
# random sample will be generated every time, so long as you always set the
# same seed beforehand
set.seed(29283)
# This data already has an Id column which we can make use of.
# Let's create our training set using sample_frac. Fill in the blank.
train_set <- train_t %>% sample_frac(.7)
# let's create our testing set using the Id column. Fill in the blanks.
test_set <- train_t %>% filter(!(train_t$PassengerId %in% train_set$PassengerId))
```

###Excercise 3
It looks as if a lower class has a high correlation with not surviving, as does being male. A higher fare indicates a slight increase in chance of survival.
```{r}
library(broom)
# Fit a model with intercept only
mod_1 <- glm(Survived ~ Pclass + Sex + Fare, data = train_set, family = 'binomial')
# take a look at the features and coefficients
tidy(mod_1)
```

###Excercise 4
A female passenger who has paid less than $26 for his fair is VERY unlikely to survive.
```{r}
tree_mod <- rpart(Survived ~ Pclass + Sex + Fare, data = train_set)
plot(as.party(tree_mod))
```

###Excercise 5
```{r}
test_logit <- predict(mod_1, newdata = test_set, type = 'response')
test_tree <- predict(tree_mod, newdata = test_set)[]

# create the prediction objects for both models
pred_logit <- prediction(predictions = test_logit, labels = test_set$Survived)
pred_tree <- prediction(predictions = test_tree, labels = test_set$Survived)
# get the FPR and TPR for the logistic model
# recall that the ROC curve plots the FPR on the x-axis
perf_logit <- performance(pred_logit, measure = 'tpr', x.measure = 'fpr')
perf_logit_tbl <- tibble(perf_logit@x.values[[1]], perf_logit@y.values[[1]])
# Change the names of the columns of the tibble
names(perf_logit_tbl) <- c('fpr', 'tpr')
# get the FPR and TPR for the tree model
perf_tree <- performance(pred_tree, measure = 'tpr', x.measure = 'fpr')
perf_tree_tbl <- tibble(perf_tree@x.values[[1]], perf_tree@y.values[[1]])
# Change the names of the columns of the tibble
names(perf_tree_tbl) <- c('fpr', 'tpr')
# Plotting function for plotting a nice ROC curve using ggplot
plot_roc <- function(perf_tbl) {
p <- ggplot(data = perf_tbl, aes(x = fpr, y = tpr)) +
geom_line(color = 'blue') +
geom_abline(intercept = 0, slope = 1, lty = 3) +
labs(x = 'False positive rate', y = 'True positive rate') +
theme_bw()
return(p)
}
# Create the ROC curves using the function we created above
plot_roc(perf_logit_tbl)
plot_roc(perf_tree_tbl)
```
```{r}
# calculate the AUC
auc_logit <- performance(pred_logit, measure = "auc")
auc_tree <- performance(pred_tree, measure = "auc")
# extract the AUC value
auc_logit@y.values[[1]]
auc_tree@y.values[[1]]
```

The two models are performing about the same.

