---
title: "Homework_2_harrison_james"
author: "James Harrison"
date: "2/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

<br>

<b>Excercise 3.2.4:</b><br>

1.I see a blank graph<br>
```{r}
ggplot(data = mpg)
```
<br><br>

2. MPG has 11 variable/rowss and 234 observations/rows<br>

3. drv means what type of drive train the vehicle has, front wheel drive, rear wheel drive, or 4 wheel drive.<br>

4. <br>
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = hwy, y = cyl))
```
<br>
<br>
5. <br>
```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = class, y = drv))
```
<br>this graph is not so useful since the scatter plot doesn't lend itself to displaying groupings. What I really want to see is what types of cars are rwd, fwd, etc. - and it takes a while to determine that.<br><br>

<b>Excercise 3.3.1</b>
<br>
1. It's missing a close parantheses so the color is being specified in the wrong spot
<br>
2. When you run MPG you can see the variable type above each column, <chr> <dbl> <int> etc. In this data set class, fl, drv, trans, manufacturer, model are chr, and numberical variables are displ, year, cyl, cty, hwy

3. <br>
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class, size = cyl, shape = fl))
```

Aesthetics behave differently - for example I couldn't assign a shape to a continuous variable. Size was not advisable to be used for categorical data.

4. <br> It lets me do it and the legend is combined automatically!
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = fl, shape = fl))
```

5. The stroke adds a border around a shape. Shapes 21-24 can have a border<br>
6. It turns it into a boolean expression - so true or false, very cool!<br>
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = displ < 5, shape = fl))
```



